Improving cropland maps through tight integration of human and machine intelligence

### 2020-03-05 manuscript/manuscript.Rmd
Recent commits

- Assessment of segmentation quality

>>>>

- Assessment of segmentation quality
- Relevant literature: 
    - [@Tongforgottenlanduse2020] discuss Sentinel-based mapping in Sahel, to detect fallows (reference to our intermediate probability values). Semi-automated approach to generating reference data from imagery (based on phenology)
    - [@BeyMappingsmallholderlargescale2020] use CollectEarth to train an algorithm. Multi-stage. No reporting of training or reference data accuracy. 
    - [@LuoDevelopingclearskycloud2008] relevant compositing method to cite, which sounds similar to ours.
